The \dealii{} Library, Version 9.4

### 2022-06-21 9.4/paper.tex
Clean up the list of contributors.
Rene is a coauthor so he and Bruno (Turcksin) should not be on this list.

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
\todo[inline]{updated 23/04/2022 PM. We should probably make sure that
  nobody else came after that and before the release.}
Pasquale	Africa,
Tyler	Anderson,
Francesco	Andreuzzi,
Mathias	Anselmann,
Maximilian	Bergbauer,
Bruno	Blais,
Till	Budde,
Fabian	Castelli,
Praveen	Chandrashekar,
Cu	Cui,
Ivo	Dravins,
Niklas	Fehn,
Johannes	Friedlein,
Sebastian	Fuchs,
Rene	Gassmoeller,
Nicola	Giuliani,
Alexander	Grayver,
Diane	Guignard,
Jake	Harmon,
Sean	Ingimarson,
Pengfei	Jia,
Sebastian	Kinnewig,
Simon	Konrad,
Katharina	Kormann,
Paras	Kumar,
Wenyu	Lei,
Alberto F.	Martin,
Nils	Much,
Lucas	Myers,
Justin	O'Connor,
Judith	Pauen,
Vachan	Potluri,
Raghunandan	Pratoori,
Sebastian	Proell,
Ce	Qin,
Reza	Rastak,
Jose E.	Roman,
Raphael	Schoof,
Magdalena	Schreter,
Konrad	Simon,
Simon	Sticko,
Bruno	Turcksin,
Kuljit S.	Virk,
Michał	Wichrowski,
Niklas Wik,
Jiaqi	Zhang.

>>>>

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%

% This is up-to-date as of 9.4 RC1 - should be the final list.
Pasquale      Africa,
Tyler         Anderson,
Francesco     Andreuzzi,
Mathias       Anselmann,
Maximilian    Bergbauer,
Manaswinee    Bezbaruah,
Bruno         Blais,
Till          Budde,
Fabian        Castelli,
Praveen       Chandrashekar,
Huimin        Chen,
Cu            Cui,
Ivo           Dravins,
Niklas        Fehn,
Corbin        Foucart,
Johannes      Friedlein,
Sebastian     Fuchs,
Daniel        Garcia-Sanchez,
Nicola        Giuliani,
Alexander     Grayver,
Diane         Guignard,
Jake          Harmon,
Sean          Ingimarson,
Pengfei       Jia,
Sebastian     Kinnewig,
Uwe           K{\"o}cher,
Katharina     Kormann,
Paras         Kumar,
Wenyu         Lei,
Alberto F.    Martin,
Nils          Much,
Lucas         Myers,
Justin        O'Connor,
Judith        Pauen,
Vachan        Potluri,
Raghunandan   Pratoori,
Sebastian     Proell,
Ce            Qin,
Reza          Rastak,
Jose E.       Roman,
Raphael       Schoof,
Magdalena     Schreter,
Konrad        Simon,
Simon         Sticko,
Daniel        Sun,
Kuljit S.     Virk,
Michał        Wichrowski,
Niklas        Wik,
Jiaqi         Zhang.
